\section{Implications for Absorber--Stripper Simulation}\label{sec:process-implications}
A thermodynamic model for loaded \MEA is useful only if it can be transferred into process calculations without losing the reactive electrolyte physics that determined the fit.  The full-ionic ePC-SAFT workflow developed here is structured for that transfer.  At each absorber or stripper stage, the property package can accept temperature, pressure, total apparent composition, and loading; solve the charge-balanced liquid speciation; evaluate ePC-SAFT activity coefficients and fugacity coefficients; and return the \COtwo equilibrium pressure or phase-equilibrium residual needed by the process model.

This coupling matters most in rich-solvent and high-temperature regions.  In an absorber, low \COtwo partial pressures require accurate lean-solvent activity and speciation predictions because small pressure errors alter the driving force for mass transfer.  In a stripper, high temperature and high loading move the system into a region where \COtwo pressure increases steeply with loading; an error in the rich-end pressure curve can therefore affect predicted reboiler duty, cyclic capacity, and solvent circulation rate.  A model that fits only the VLE curve but gives an incorrect carbamate/bicarbonate distribution can still give misleading heat-release and solvent-capacity trends.

The immediate process-simulation interface should expose three outputs: the \COtwo equilibrium partial pressure, the liquid true-species composition, and the activity/fugacity diagnostics used to verify thermodynamic consistency.  These outputs are sufficient for a rate-based absorber model, an equilibrium-stage stripper calculation, or a reduced solvent-cycle analysis.  A later column case study should compare the full ionic ePC-SAFT solvent model against an activity-coefficient baseline under the same flue-gas composition, lean loading, solvent flow rate, and temperature profile.  The most meaningful process metrics will be predicted \COtwo removal, rich loading, lean loading, equilibrium approach along the column, and energy sensitivity to the fitted electrolyte parameters.

The current first-draft article therefore treats the process section as a translation of the thermodynamic model into a process-simulation contract.  Once the final parameter regression is complete, this section should be extended with a numerical absorber or stripper demonstration using the fitted full-ionic ePC-SAFT property package.
