\section{Conclusions}\label{sec:conclusion}
This work evaluates \COtwo solubility in loaded aqueous \MEA with an explicit true-species thermodynamic basis and SSM+DS modified-Born ePC-SAFT.  Literature VLE solubility data and NMR speciation data were assembled on a common \COtwo-loading basis, transformed into a charge-balanced liquid representation, and evaluated with both an ideal Smith--Missen-style baseline and an activity-coupled ePC-SAFT calculation.  The activity-based calculation includes ePC-SAFT activities and fugacities, concentration-dependent permittivity, and SSM+DS Born solvation terms, so changes in \COtwo loading affect both liquid speciation and ion solvation.

The ideal-equilibrium baseline reproduces the main amine and bicarbonate speciation trends while exposing the temperature dependence of the solubility-pressure baseline.  The reported major-species median absolute \(\log_{10}\) residuals are 0.055 for \MEA, 0.044 for \MEAH, 0.029 for \MEACOO, 0.227 for \HCOthree, and 0.0087 for \ce{MEA + MEAH+}.  The 40 and \SI{60}{\degreeCelsius} pressure rows have larger deviations than the higher-temperature rows, so the baseline is retained as a reaction and balance convention check rather than as the final activity-based solubility result.

In the controlled 31-row pressure comparison, the median absolute \(\log_{10}(P_{\mathrm{model}}/P_{\mathrm{data}})\) residual is 0.160 for the ideal baseline and 0.495 for the activity calculation; for this fixed parameterization, the activity model is less accurate on the common records.  The activity-coupled ePC-SAFT calculation separately converged for all 161 \COtwo-solubility pressure records and 74 speciation records.  Its six-source contextual pressure residual is 0.493 on the median absolute \(\log_{10}\) scale, but pressure uncertainty is unavailable and the full set is not a direct comparator for the 31-row baseline.  Nonzero measured-target speciation residuals are 0.074 for \MEA, 0.033 for \MEAH, 0.040 for \MEACOO, 0.461 for \HCOthree, and 0.066 for \ce{MEA + MEAH+}.  Reporting these pressure and speciation residuals together prevents the fixed parameter set from being interpreted as a pressure-only solubility fit.  The 15 reported-zero targets remain below a modeled \HCOthree mole-fraction upper bound of 0.00128.  Carbonate and trace water-ion quantities remain the limiting species family.

The strongest defensible claim is therefore an evaluation claim rather than a parameter-estimation claim.  \MEAH and \MEACOO are directly observed in \MEA-system speciation data and represent the carbamate-forming chemistry that distinguishes \MEA from tertiary-amine MDEA systems, but their retained values remain provisional fixed inputs.  Carbonate-family and water autoionization ions rely on literature-backed values, sensitivity checks, and charge-balance constraints.  The bicarbonate/carbonate Born sensitivity should be read as an identifiability boundary for transferring SSM+DS modified-Born ePC-SAFT to loaded \MEA, not as a pressure-model failure alone.  The present work does not report a completed coupled solubility/speciation regression.  The reported parameter set is evaluated with explicit residuals, not presented as a newly fitted VLE or speciation parameterization.
