\section{Data and Methods}\label{sec:data-methods}

\subsection{Experimental Solubility and Speciation Data}
The \COtwo-solubility data set contains 161 equilibrium partial-pressure records compiled from six VLE sources\cite{Aronu2011,Hilliard2008,Idris2014,Jou1995,Mamun2005,Xu2011}.  Each canonical record retains a stable source key, source filename, and one-based source-row identity in addition to amine mass fraction, temperature, \COtwo loading, and measured \COtwo pressure.  The aggregate is generated from a row-level inclusion manifest; six Xu records carry explicit nominal-temperature normalization from 100.5--\SI{101.1}{\degreeCelsius} to \SI{100}{\degreeCelsius} or 120.4--\SI{121.8}{\degreeCelsius} to \SI{120}{\degreeCelsius}.  The speciation data set contains 74 NMR-derived liquid-composition records compiled from three spectroscopic studies\cite{Bottinger2008,Jakobsen2005,Matin2012}.  The speciation records are expressed on a common loading basis and reconciled to satisfy carbon, amine, water, and charge balances before model comparison.

\begin{center}
    \begin{minipage}{\linewidth}
    \centering
    \captionsetup{hypcap=false}
    \captionof{table}{Experimental evidence base used for the \MEA \COtwo-solubility and speciation evaluation.}
    \label{tab:mea-data-inventory}
    \small
    \begin{tabularx}{\linewidth}{lclXX}
        \toprule
        Data family & Records & Primary sources & Conditions & Observables and residual role \\
        \midrule
        VLE & 161 & \cite{Aronu2011,Hilliard2008,Idris2014,Jou1995,Mamun2005,Xu2011} &
        30 wt\% \MEA, 40--\SI{120}{\degreeCelsius}, \(\alpha=0.003\)--0.689, \(P_{\COtwo}=1.5\times10^{-3}\)--\(2.804\times10^3\) kPa &
        Measured \COtwo pressure at fixed loading; logarithmic solubility residual \\
        Speciation & 74 & \cite{Bottinger2008,Jakobsen2005,Matin2012} &
        30 wt\% \MEA, 20--\SI{80}{\degreeCelsius}, \(\alpha=0.064\)--0.990 &
        True-species mole fractions; direct-positive, reported-zero, and balance-inferred target roles \\
        \bottomrule
    \end{tabularx}
    \end{minipage}
\end{center}

\subsection{Species Basis and Parameter Hierarchy}
The activity-based calculation uses the nine-species liquid basis defined in \cref{eq:true-species-vector}.  The parameter hierarchy separates inherited molecular parameters, SSM+DS ion conventions from modified-Born ePC-SAFT literature, provisional fixed inputs for \MEAH and \MEACOO, and trace-ion quantities retained from literature-backed or diagnostic calculations.  This hierarchy is used to evaluate a fixed advanced-Born parameter set for \COtwo-solubility modeling; it is not a pressure-only fitted model.

\input{tables/full_ionic_ssm_ds_parameters}

The parameter-evidence matrix in \cref{tab:parameter-evidence-matrix,tab:trace-parameter-evidence} distinguishes the evidentiary status of the retained inputs from trace-species quantities that are not independently identified by the available NMR targets.  The available speciation data test \MEAH and \MEACOO most directly; bicarbonate, carbonate, hydronium, and hydroxide quantities require additional caution because they are constrained by fewer direct targets or by balance relationships.

\input{tables/parameter_evidence_matrix}

\subsection{Pure-Component and Binary Parameters}
The molecular \COtwo, \MEA, and \HtwoO parameters are inherited from the cited PC-SAFT and ePC-SAFT sources listed in \cref{tab:full-ionic-ssm-ds-parameters}.  The temperature-dependent water segment diameter is
\begin{equation}
    \sigma_{\HtwoO}(T)=2.7927+10.11\exp(-0.01775T)-1.417\exp(-0.01146T),
    \label{eq:water-sigma-temperature}
\end{equation}
where \(T\) is in kelvin and \(\sigma_{\HtwoO}\) is in angstroms.  The final column of \cref{tab:full-ionic-ssm-ds-parameters} reports a source or status for every retained value; provisional inputs are explicitly distinguished from literature values.

The binary-interaction matrix is intentionally sparse.  \Cref{tab:binary-interaction-parameters} lists the nonzero interactions, the zero-valued candidate interactions retained for the fixed activity-based evaluation, and the transferred water--ion terms.  The remaining \MEA-specific ion--molecule and ion--ion terms are held at zero.  This sparse interaction structure tests the selected activity model before introducing a broader optimized binary-interaction matrix.

\input{tables/binary_interaction_parameters}

\subsection{Fixed parameter evidence boundary}
The coupled native regression was not completed.  The retained \MEAH and \MEACOO values are provisional fixed inputs inherited from an exploratory historical calculation, not a reproducible parameter fit executed by the current workflow.  The NMR/speciation studies\cite{Matin2012,Jakobsen2005,Bottinger2008} are therefore used only to evaluate the resulting fixed-parameter speciation residuals.  Historical local-fit bounds, improvement metrics, and parity plots are excluded because they do not establish a current parameter-estimation result.  A future parameter claim requires an executed package-native, multi-observable regression with complete row provenance and held-out evidence defined before fitting.

\subsection{Coupled CO2 Solubility and Speciation Objective}
The pressure residual is expressed on a logarithmic basis,
\begin{equation}
    \epsilon_{P,j}
    =
    \log_{10}\left(\frac{P_{\COtwo,j}^{\mathrm{model}}}{P_{\COtwo,j}^{\mathrm{exp}}}\right),
    \label{eq:pressure-log-residual}
\end{equation}
because measured \COtwo partial pressures span several orders of magnitude across the solubility data.  Speciation residuals use the same \(\log_{10}(\mathrm{model}/\mathrm{data})\) form for nonzero measured targets.  Measurements reported as zero and treated as upper-bound targets are evaluated separately with modeled mole-fraction upper bounds, and quantities inferred from balance constraints are used as context rather than direct logarithmic targets.

The multi-observable target combines pressure residuals, speciation residuals, reaction-equilibrium residuals, and regularization to the parameter seed:
\begin{equation}
    \begin{aligned}
    \Phi(\boldsymbol{\theta}) ={}&
    \sum_{j\in\mathcal{D}_P} w_{P,j}\epsilon_{P,j}^{2} \\
    &+
    \sum_{j\in\mathcal{D}_x}\sum_{i\in\mathcal{S}_x} w_{x,ij}
    \left[\log_{10}\left(\frac{x_{ij}^{\mathrm{model}}}{x_{ij}^{\mathrm{exp}}}\right)\right]^2 \\
    &+
    \sum_{j\in\mathcal{D}_x}\sum_r w_{K,rj}
    \left(\sum_i \nu_{ri}\ln a_{ij}-\ln K_r(T_j)\right)^2 \\
    &+
    \lambda\lVert \boldsymbol{\theta}-\boldsymbol{\theta}_0\rVert^2 .
    \end{aligned}
    \label{eq:regression-objective}
\end{equation}
The \(K_r(T)\) values are the fixed reaction constants listed in \cref{tab:reaction-equilibrium-constants}.  A solubility-pressure-only fit can hide a poor liquid composition, while a speciation-only fit cannot guarantee the correct vapor-phase pressure.  A thermodynamic model intended for reactive \COtwo solubility and liquid speciation must therefore satisfy both observable families.

\subsection{Computational implementation and reproducibility}
The baseline calculation is an ideal Smith--Missen-style five-reaction, nine-species equilibrium solve with activities set equal to mole fractions.  The activity-based calculation evaluates the same reaction network with ePC-SAFT activities, fugacities, concentration-dependent permittivity, and SSM+DS Born corrections.  The present work does not report a completed coupled solubility/speciation regression.  The reported parameter set is therefore evaluated as a fixed activity-based parameter set with explicit pressure and speciation residuals.  \Cref{tab:residual-summary} summarizes the residual metrics that define the manuscript claims.

\input{tables/residual_summary}
