\section{Thermodynamic Model and Residual Evaluation}\label{sec:model-framework}
The modeling target is a reacting electrolyte vapor--liquid equilibrium problem.  At specified temperature, apparent amine concentration, and total absorbed \COtwo loading, the model must determine a charge-balanced true-species liquid composition and the corresponding vapor-phase \COtwo partial pressure.  The liquid composition is not an auxiliary bookkeeping variable; it controls ePC-SAFT fugacity coefficients, activity coefficients, and Born/electrostatic contributions.

\subsection{ePC-SAFT Residual Helmholtz Energy}
ePC-SAFT is formulated as a residual Helmholtz-energy equation of state.  For a state defined by temperature \(T\), molar density \(\rho\), and mole-fraction vector \(\boldsymbol{x}\), the reduced residual Helmholtz energy \(\tilde{a}^{\mathrm{res}}=a^{\mathrm{res}}/(RT)\) is assembled from hard-chain, dispersion, association, Debye--Huckel, and Born terms \cite{Gross2001,Gross2002,Cameretti2005,Bulow2021a,Figiel2025}:
\begin{equation}
    \tilde{a}^{\mathrm{res}}
    =
    \tilde{a}^{\mathrm{hc}}
    +\tilde{a}^{\mathrm{disp}}
    +\tilde{a}^{\mathrm{assoc}}
    +\tilde{a}^{\mathrm{DH}}
    +\tilde{a}^{\mathrm{Born}} ,
    \label{eq:epcsaft-residual-split}
\end{equation}
where the hard-chain contribution gives the repulsive chain reference, the dispersion contribution gives short-range attraction, the association contribution gives site-specific hydrogen bonding, the Debye--Huckel term gives long-range electrostatics, and the Born term gives electrostatic solvation.  Neutral \MEA and \HtwoO therefore require segment, dispersion, and association parameters, whereas charged species also require charge, dielectric, and Born-diameter information.

The hard-chain reference is built from packing-fraction moments
\begin{equation}
    \zeta_n=\frac{\pi}{6}\rho\sum_i x_i m_i d_i^n,\qquad n\in\{0,1,2,3\},
    \label{eq:epcsaft-zeta-moments}
\end{equation}
where \(m_i\) is the segment number and \(d_i\) is the temperature-dependent segment diameter.  With \(\bar{m}=\sum_i x_i m_i\), the chain correction subtracts the connectivity penalty from the hard-sphere reference,
\begin{equation}
    \tilde{a}^{\mathrm{hc}}
    =
    \bar{m}\tilde{a}^{\mathrm{hs}}
    -
    \sum_i x_i(m_i-1)\ln g_{ii}^{\mathrm{hs}}(\sigma_{ii}) .
    \label{eq:epcsaft-hard-chain}
\end{equation}
This term controls excluded volume and the density scale used by all subsequent residual derivatives.

The dispersion term introduces attractive perturbations through mixture moments of segment energy and size,
\begin{equation}
    \tilde{a}^{\mathrm{disp}}
    =
    -2\pi\rho I_1(\eta,\bar{m})\overline{m^2\epsilon\sigma^3}
    -\pi\rho\bar{m}C_1 I_2(\eta,\bar{m})
    \overline{m^2\epsilon^2\sigma^3},
    \label{eq:epcsaft-dispersion}
\end{equation}
where \(\eta=\zeta_3\), \(I_1\) and \(I_2\) are the PC-SAFT dispersion integrals, and the overbars denote the corresponding pair-mixed composition averages.  Binary interaction parameters enter this contribution through the mixed dispersion energy \(\epsilon_{ij}\), so pressure residuals can be sensitive to neutral--neutral and ion--molecule dispersion choices.

Association is represented through site fractions \(X^{A_i}\),
\begin{equation}
    \tilde{a}^{\mathrm{assoc}}
    =
    \sum_i x_i \sum_{A_i}
    \left[
        \ln X^{A_i}
        -\frac{X^{A_i}}{2}
        +\frac{1}{2}
    \right],
    \label{eq:epcsaft-association}
\end{equation}
with association strengths proportional to
\begin{equation}
    \Delta^{A_iB_j}_{ij}
    =
    d_{ij}^{3}g_{ij}^{\mathrm{hs}}
    \kappa^{A_iB_j}_{ij}
    \left[
        \exp\left(\frac{\epsilon^{A_iB_j}_{ij}}{k_{\mathrm{B}}T}\right)-1
    \right].
    \label{eq:epcsaft-association-strength}
\end{equation}
This is the contribution that carries the hydrogen-bonding physics of water and alkanolamines; it is absent for ions without association sites.

For charged species, the Debye--Huckel contribution uses the dielectric state and the inverse Debye length,
\begin{align}
    \kappa
    &=
    \left[
        \frac{\rho e^2}{k_{\mathrm{B}}T\varepsilon_0\varepsilon_r}
        \sum_j x_j z_j^2
    \right]^{1/2},
    \label{eq:epcsaft-debye-kappa} \\
    \tilde{a}^{\mathrm{DH}}
    &=
    -\frac{\kappa e^2}{12\pi\varepsilon_0\varepsilon_r k_{\mathrm{B}}T}
    \sum_i x_i z_i^2\chi_i ,
    \label{eq:epcsaft-debye-helmholtz}
\end{align}
where \(z_i\) is the ionic charge and \(\chi_i\) is the finite-ion-size correction.  The same relative permittivity \(\varepsilon_r\) also enters the Born term, making the dielectric rule a coupled electrostatic input rather than a separate post-processing correction.

The Born contribution is evaluated in modular form:
\begin{equation}
    \tilde{a}^{\mathrm{Born}}
    =
    -\frac{e^2}{4\pi\varepsilon_0 k_{\mathrm{B}}T}
    \sum_i x_i z_i^2
    \sum_{\delta\in\mathcal{D}}
    \left(1-\frac{1}{\varepsilon_{r,m_\delta}}\right)
    D_{i,\delta}^{(m_\delta)} .
    \label{eq:epcsaft-born-modular}
\end{equation}
The active set \(\mathcal{D}\) always contains the base Born term and may also include the solvation-shell-modeling (SSM) and dielectric-saturation (DS) corrections,
\begin{equation}
    \mathcal{D}
    =
    \{\mathrm{Born}\}\cup\mathcal{D}_{\mathrm{add}},
    \qquad
    \mathcal{D}_{\mathrm{add}}\subseteq\{\mathrm{SSM},\mathrm{DS}\}.
    \label{eq:epcsaft-born-active-set}
\end{equation}
For the SSM+DS option used in this work, \(\mathcal{D}_{\mathrm{add}}=\{\mathrm{SSM},\mathrm{DS}\}\).  The base Born and SSM terms use the bulk dielectric medium, while the DS term uses the ion-local dielectric medium:
\begin{equation}
    m_\delta=
    \begin{cases}
        \mathrm{bulk}, & \delta\in\{\mathrm{Born},\mathrm{SSM}\},\\
        \mathrm{ion}, & \delta=\mathrm{DS}.
    \end{cases}
    \label{eq:epcsaft-born-medium}
\end{equation}
The inverse-diameter terms are
\begin{align}
    D_{i,\mathrm{Born}}^{(\mathrm{bulk})}
    &=
    \frac{1}{d_i^{\mathrm{Born}}},
    \label{eq:epcsaft-born-base-dterm}\\
    D_{i,\mathrm{SSM}}^{(\mathrm{bulk})}
    &=
    \frac{1}{d_i^{\mathrm{Born}}+\Delta d_i}
    -
    \frac{1}{d_i^{\mathrm{Born}}},
    \label{eq:epcsaft-born-ssm-dterm}\\
    D_{i,\mathrm{DS}}^{(\mathrm{ion})}
    &=
    \frac{1}{d_i^{\mathrm{Born}}}
    -
    \frac{1}{d_i^{\mathrm{Born}}+\Delta d_i},
    \label{eq:epcsaft-born-ds-dterm}
\end{align}
with shell shift
\begin{equation}
    \Delta d_i
    =
    \frac{f_{\mathrm{mix}}-1}{|z_i|}\,d_i^{\mathrm{Born}},
    \qquad
    f_{\mathrm{mix}}=\sum_k x_k f_k .
    \label{eq:epcsaft-born-shell-shift}
\end{equation}
The SSM term changes the effective Born radius used with the bulk medium, whereas the DS term transfers the complementary radius increment into the ion-local dielectric medium.  This split is important for loaded \MEA because carbonation changes both the ionic population and the solvent environment.

For a liquid state at temperature $T$, pressure $P$, and mole-fraction vector $\boldsymbol{x}$, ePC-SAFT provides residual chemical potentials and fugacity coefficients.  Molecular vapor--liquid equilibrium is expressed through fugacity equality,
\begin{equation}
    f_i^{\liq}(T,P,\boldsymbol{x}^{\liq})
    =
    f_i^{\vap}(T,P,\boldsymbol{y}^{\vap}),
    \qquad i \in \{\COtwo,\HtwoO,\MEA\},
    \label{eq:fugacity-equality}
\end{equation}
while ionic species are constrained to the liquid phase.  The residual Helmholtz contribution enters this relation through
\begin{equation}
    \ln\varphi_k
    =
    \tilde{\mu}_k^{\mathrm{res}}-\ln Z,
    \qquad
    \ln\gamma_i^{*}
    =
    \ln\varphi_i-\ln\varphi_i^{\infty},
    \label{eq:epcsaft-phi-gamma-link}
\end{equation}
so each residual contribution affects both phase equilibrium and the activity coefficients used in the true-species reaction equations.

\subsection{True-Species Chemical Equilibrium}
The apparent feed is defined by the unloaded \MEA mass fraction $w_{\MEA}$ and \COtwo loading $\alpha$, with $\alpha$ equal to moles of absorbed \COtwo per mole of total amine.  The unloaded apparent liquid composition is computed from molecular-weight conversion as
\begin{equation}
    x_{\MEA,0}
    =
    \frac{w_{\MEA}}
    {M_{\MEA}/M_{\HtwoO}+w_{\MEA}\left(1-M_{\MEA}/M_{\HtwoO}\right)},
    \qquad
    x_{\HtwoO,0}=1-x_{\MEA,0}.
    \label{eq:unloaded-mea-composition}
\end{equation}
Absorbed \COtwo is then added according to $n_{\COtwo,0}=\alpha n_{\MEA,0}$ and the total apparent state is normalized.

The true-species liquid basis is
\begin{equation}
    \boldsymbol{x}
    =
    \left(
    x_{\COtwo},x_{\MEA},x_{\HtwoO},x_{\MEAH},x_{\MEACOO},
    x_{\HCOthree},x_{\COthree},x_{\HthreeO},x_{\Hydroxide}
    \right).
    \label{eq:true-species-vector}
\end{equation}
The independent reactions include water autoionization, carbonic-acid dissociation to bicarbonate and carbonate, carbamate hydrolysis, and protonated-amine dissociation.  For reaction $r$, thermodynamic equilibrium is written with activities rather than bare mole fractions,
\begin{equation}
    \sum_i \nu_{ri}\ln a_i = \ln K_r(T),
    \qquad
    a_i = \gamma_i^{\mathrm{ePC-SAFT}} x_i,
    \label{eq:activity-reaction-equilibrium}
\end{equation}
where $\nu_{ri}$ is the stoichiometric coefficient and $\gamma_i^{\mathrm{ePC-SAFT}}$ is the activity coefficient evaluated from the ePC-SAFT liquid state.  This activity-coupled form is the key distinction from the ideal-equilibrium baseline.

The liquid composition also satisfies carbon, amine, water, and charge balances:
\begin{align}
    x_{\COtwo,0} &= x_{\COtwo}+x_{\MEACOO}+x_{\HCOthree}+x_{\COthree}, \\
    x_{\MEA,0} &= x_{\MEA}+x_{\MEAH}+x_{\MEACOO}, \\
    x_{\HtwoO,0} &= x_{\HtwoO}+x_{\HCOthree}+x_{\COthree}+x_{\HthreeO}+x_{\Hydroxide}, \\
    x_{\MEAH}+x_{\HthreeO} &= x_{\MEACOO}+x_{\HCOthree}+2x_{\COthree}+x_{\Hydroxide}.
    \label{eq:true-species-balances}
\end{align}

\subsection{Advanced Born and Permittivity Treatment}
The ePC-SAFT calculations in this work use concentration-dependent permittivity and modified Born solvation.  The electrolyte model uses an empirical relative-permittivity rule, Born-radius mode 3, solvation-shell modeling, dielectric saturation, and composition-dependent Born chemical-potential corrections.  This is the SSM+DS form introduced for the modified Born contribution, in which an ion-specific Born diameter is combined with a solvent-shell correction and a radially simplified dielectric-saturation term \cite{Figiel2025}.  The corresponding ePC-SAFT literature treats the pure-ion relative permittivity as $\varepsilon_r=8$, sets $f_k=1$ for ions, and fits the solvent $f_k$ parameter to electrolyte activity data; water, methanol, and ethanol have reported $f_k$ values of 1.5, 1.4, and 1.6, respectively \cite{Figiel2025}.  Loaded 30 wt\% \MEA also has direct dielectric-dispersion measurements, which show that static permittivity changes with both temperature and carbonation ratio \cite{Hajj2024}.  Those data motivate, but do not yet fully identify, an MEA-specific solvent-shell parameter.

In physical terms, the liquid dielectric environment is not treated as a fixed pure-water constant.  Instead, the ion solvation contribution responds to solvent composition and ionic strength, which is essential for a loaded amine solution whose polarity and ion population change strongly with \COtwo loading.  The parameter table in \cref{tab:full-ionic-ssm-ds-parameters} therefore distinguishes fitted MEA-family ion parameters from SSM+DS conventions transferred from electrolyte literature.

\subsection{Residual Metrics and Parameter Status}
The parameter vector $\boldsymbol{\theta}$ includes selected pure-component parameters for \MEA-family species and selected binary interaction parameters.  The pressure residual is expressed on a logarithmic basis,
\begin{equation}
    \epsilon_{P,j}
    =
    \log_{10}\left(\frac{P_{\COtwo,j}^{\mathrm{model}}}{P_{\COtwo,j}^{\mathrm{exp}}}\right),
    \label{eq:pressure-log-residual}
\end{equation}
because measured \COtwo partial pressures span several orders of magnitude.  The full regression target combines pressure residuals, speciation residuals, reaction-equilibrium residuals, and regularization to physically plausible seeds:
\begin{equation}
    \Phi(\boldsymbol{\theta}) =
    \sum_{j\in\mathcal{D}_P} w_{P,j}\epsilon_{P,j}^{2}
    +
    \sum_{j\in\mathcal{D}_x}\sum_{i\in\mathcal{S}_x} w_{x,ij}
    \left[\log_{10}\left(\frac{x_{ij}^{\mathrm{model}}}{x_{ij}^{\mathrm{exp}}}\right)\right]^2
    +
    \sum_{j\in\mathcal{D}_x}\sum_r w_{K,rj}
    \left(\sum_i \nu_{ri}\ln a_{ij}-\ln K_r\right)^2
    +
    \lambda\lVert \boldsymbol{\theta}-\boldsymbol{\theta}_0\rVert^2.
    \label{eq:regression-objective}
\end{equation}
This objective is multi-observable.  A pressure-only fit can hide a poor liquid composition, while a speciation-only fit cannot guarantee the correct gas-phase driving force.  A jointly regressed predictive model must satisfy both.

\input{tables/regression_bounds}

In the present calculation, the direct \MEAH/\MEACOO speciation fit is reproducible and is reported as part of the parameter evidence.  The all-row coupled pressure/speciation regression is not reported as a completed parameter optimization because the available ePC-SAFT regression method does not yet provide the sensitivity information needed to accept a joint fit.  We therefore report the target set, the parameter window in \cref{tab:regression-bounds}, and the residual-qualified activity-based evaluation, rather than presenting a pressure-optimized global parameter set.



