\section{Introduction}\label{sec:introduction}
\COtwo solubility in aqueous alkanolamines is a central thermodynamic quantity for carbon-capture solvents.  Monoethanolamine (\MEA) remains the reference aqueous amine because it has a long record of use and a broad experimental literature.  Its solubility behavior is challenging because absorbed \COtwo does not remain a neutral dissolved gas.  It reacts with water and amine to form a liquid mixture containing molecular species, protonated amine, carbamate, bicarbonate, carbonate, hydronium, and hydroxide.  The equilibrium \COtwo partial pressure at a given loading is therefore coupled to both phase equilibrium and chemical speciation.

Natural-gas processing provides a related upstream capture setting.  Raw natural gas contains variable amounts of nonhydrocarbon components, including \COtwo, \ce{H2S}, and water vapor, that are removed before sales-gas delivery or end use~\cite{EIA2026NaturalGasExplained}.  Natural-gas processing is also identified as a high-purity industrial \COtwo source because \COtwo removal can be inherent to gas processing, with reported discharge-stream compositions of 96--99\% \COtwo in representative assessments~\cite{NETL2022IndustrialCO2CaptureCosts}.  In that setting, \COtwo separation occurs before combustion of the methane-rich product rather than after combustion in a dilute flue gas.  Capture guidance identifies chemical solvents, including \MEA and methyldiethanolamine (MDEA), for \COtwo removal from natural gas or shifted syngas~\cite{IPCC2005SRCCSChapter3}, and the Sleipner project demonstrates geological storage of \COtwo separated from produced natural gas~\cite{Equinor2026CCUS}.  This upstream context reinforces the need for thermodynamic models that couple \COtwo loading, liquid speciation, and phase equilibrium: the same solvent-loading and ionic-composition variables that control post-combustion amine absorption also govern acid-gas removal from natural gas.

In reactive vapor--liquid equilibrium, \COtwo solubility is commonly represented by the \COtwo partial-pressure/loading relation.  That relation and the liquid speciation are coupled observables of the same thermodynamic state.  The pressure tests the gas--liquid fugacity balance, whereas speciation tests the acid--base reaction equilibria, material balances, and electroneutrality constraint.  A pressure-only solubility fit can therefore reproduce a pressure curve while hiding an implausible distribution of \MEA, \MEAH, \MEACOO, \HCOthree, and \COthree species.  For that reason, this work evaluates \COtwo solubility and speciation together.

\subsection{CO2 solubility in reactive MEA}
Loaded aqueous \MEA is a reactive electrolyte solution, not a simple physical-solubility system.  The apparent variables used in many data sets, such as unloaded amine mass fraction and \COtwo loading, must be reconciled with a true-species liquid composition before an equation of state can evaluate fugacities or activity coefficients.  The experimental basis used here combines vapor--liquid-equilibrium (VLE) measurements of \COtwo partial pressure with nuclear magnetic resonance (NMR) measurements of liquid-phase species.  These data families are complementary: VLE data define the \COtwo-solubility pressure response, whereas speciation data constrain whether the liquid composition remains chemically plausible.

\subsection{Thermodynamic modeling of CO2 solubility in MEA--CO2--H2O}
Thermodynamic descriptions of \COtwo-loaded amines have historically relied on apparent-species correlations or activity-coefficient models.  Kent--Eisenberg and related apparent-equilibrium approaches provide compact correlations but have limited transferability outside their fitted temperature, loading, and solvent-composition windows.  Electrolyte-NRTL and related excess-Gibbs-energy models improved the representation of ionic liquid nonideality for \MEA--\COtwo--\HtwoO systems\cite{Zhang2011,Morgan2017b,Mouhoubi2020,Hilliard2008}.  These models remain useful reference descriptions, but their reliability depends strongly on fitted interaction parameters and on the species convention used for regression.

The \MEA literature contains enough pressure and speciation measurements to test a more molecularly explicit description of \COtwo solubility.  VLE measurements provide \COtwo partial pressures across temperature, loading, and amine-composition conditions\cite{Jou1995,Hilliard2008,Mamun2005,Xu2011,Aronu2011}.  NMR measurements provide independent liquid-phase speciation constraints for \MEA, \MEAH, \MEACOO, \HCOthree, and carbonate-containing species\cite{Jakobsen2005,Bottinger2008,Matin2012}.  A thermodynamic model intended for reactive \COtwo solubility should therefore report both gas-phase pressure residuals and liquid-speciation residuals.

\subsection{SAFT and PC-SAFT models for CO2 solubility}
Statistical associating fluid theory (SAFT)-type equations of state provide an alternative to purely excess-Gibbs-energy descriptions because molecular size, dispersion, chain formation, and association are represented in the Helmholtz-energy model.  The perturbed-chain statistical associating fluid theory (PC-SAFT) equation of Gross and Sadowski introduced a perturbation theory for chain molecules\cite{Gross2001}, and its associating extension provides the site-based hydrogen-bonding contribution needed for water and alkanolamines\cite{Gross2002}.  PC-SAFT has been applied directly to aqueous ethanolamine systems and acid-gas solubility, including pure alkanolamine property regression and VLE prediction for aqueous amines\cite{Nasrifar2010}.  Baygi and Pahlavanzadeh applied PC-SAFT to \COtwo solubility in aqueous \MEA, using a chemical-equilibrium step to reconstruct liquid species and a neutral PC-SAFT pressure calculation as the phase-equilibrium model\cite{Baygi2015}.  Other SAFT variants have also been used for loaded \MEA, including transferable SAFT-VR models that represent chemisorption stoichiometry through effective association sites\cite{MacDowell2010}.  More recent SAFT comparisons for alkanolamines continue to show that EOS-based models can describe pure, binary, and ternary amine properties with physically interpretable parameters\cite{Pakravesh2025a}.

These studies establish the relevance of SAFT-family models for amine thermodynamics, but most PC-SAFT treatments of loaded \MEA either use an apparent chemistry representation or handle the reactive liquid composition outside the electrolyte EOS.  The resulting liquid composition is then passed to the phase-equilibrium calculation rather than solved with ionic activity coefficients from the same electrolyte EOS.  This separation is especially limiting for \MEA because carbamate formation creates the \MEAH/\MEACOO ion pair that does not appear in tertiary-amine MDEA chemistry.

\subsection{ePC-SAFT and advanced Born electrostatics}
Electrolyte PC-SAFT (ePC-SAFT) extends PC-SAFT to charged species by adding an electrolyte contribution to the residual Helmholtz energy.  The original aqueous-electrolyte formulation introduced Debye--Huckel electrostatic effects into the PC-SAFT framework and demonstrated correlations for aqueous salt densities and vapor pressures\cite{Cameretti2005}.  Uyan et al. applied ePC-SAFT to aqueous MDEA--\COtwo solubility with explicit ionic species and activity-coupled chemical equilibrium, treating the calculation as predictive when no binary parameters were adjusted to the ternary acid-gas data\cite{Uyan2015}.  Wangler et al. extended that amine-solubility strategy by fitting selected binary interactions to independent osmotic-coefficient data and validating the resulting model against acid-gas solubility, thereby distinguishing literature-collected pure-component parameters, independently regressed binary parameters, and final VLE validation data\cite{Wangler2018}.

Later ePC-SAFT developments addressed non-aqueous and mixed-solvent electrolytes, where ion solvation and composition-dependent permittivity become central.  The ePC-SAFT advanced formulation of Buelow, Ascani, and Held incorporated a concentration-dependent dielectric constant into both the Born contribution and Debye--Huckel term\cite{Bulow2020}; the second part extended the framework to salt solubility and ion pairing\cite{Bulow2021}.  Subsequent work used ePC-SAFT advanced to predict \COtwo solubility in aqueous and organic electrolyte solutions, including systems with carbonate chemistry\cite{Schick2023}.  More recent studies refined the modified-Born term through solvation-shell modeling and dielectric saturation (SSM+DS), which add ion-local solvation structure to the Born contribution\cite{Rueben2024,Figiel2025}.

Loaded aqueous \MEA is a direct test for this model class because \COtwo loading changes the ionic population, the solvent dielectric environment, and the amount of carbamate formed from the primary amine.  The system contains associating neutral molecules, molecular \COtwo, large solvent-composition changes, and multiple ionic products of acid--base chemistry.  A true-species SSM+DS ePC-SAFT model can therefore connect phase equilibrium, reaction equilibrium, ionic activity coefficients, and composition-dependent solvation in one thermodynamic framework.

\input{tables/literature_model_comparison}

\subsection{Contribution of this work}
This work extends SSM+DS modified-Born ePC-SAFT to reactive aqueous \MEA--\HtwoO--\COtwo solubility.  Prior \MEA PC-SAFT studies reconstructed liquid chemistry outside the electrolyte EOS, whereas the present calculation resolves a nine-species ionic liquid basis and couples reaction equilibria to ePC-SAFT activities, fugacities, concentration-dependent permittivity, and modified Born solvation.  The \MEA-family ion parameters for \MEAH and \MEACOO are constrained with NMR speciation data, and the fixed parameter set is evaluated against both \COtwo partial-pressure and liquid-speciation records.  The result is a residual-qualified advanced-Born ePC-SAFT test for loaded \MEA, with carbonate-family Born parameters identified as the main remaining limitation.
