\begingroup
\scriptsize
\setlength{\tabcolsep}{2pt}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.10\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.38\linewidth}}
\caption{Parameter-evidence matrix for the full ionic MEA ePC-SAFT basis.}\label{tab:parameter-evidence-matrix}\\
\toprule
Species & Parameter scope & Evidence status & Data or basis \\
\midrule
\endfirsthead
\toprule
Species & Parameter scope & Evidence status & Data or basis \\
\midrule
\endhead
CO2 & \makecell[l]{m, s, e, dielc,\\MW} & molecular PC-SAFT seed & Non-electrolyte CO2 parameterization used as the inherited molecular component. \\
MEA & \makecell[l]{m, s, e, e\_assoc,\\vol\_a, assoc\_scheme,\\MW} & molecular PC-SAFT seed & Associating neutral amine parameterization retained as the MEA molecular basis. \\
MEA & f\_solv & not included as an adjusted MEA solvent-shell parameter & Figiel et al. report solvent $f_k$ values near 1.5 for water and alcohol solvents, but an MEA transfer value degraded the speciation calculation; the adopted parameter set therefore keeps $f\_solv=1$ pending direct MEA dielectric and activity regression. \\
H2O & \makecell[l]{m, s(T), e, e\_assoc,\\vol\_a, dielc, f\_solv,\\MW} & SSM+DS solvent parameter & Water PC-SAFT parameters and SSM+DS $f_k=1.5$ from modified Born ePC-SAFT literature. \\
MEAH+ & \makecell[l]{s, e,\\d\_born} & fitted to MEA speciation data & Direct MEAH+ NMR/speciation targets in Tier A local data. \\
MEAH+ & \makecell[l]{dielc, f\_solv,\\z, MW} & ionic conventions & All ions use relative dielectric constant 8 and $f\_solv=1$ in SSM+DS; charge and molecular weight come from the species definition. \\
MEACOO- & \makecell[l]{s, e, d\_born,\\k\_ij(MEAH+,\\MEACOO-)} & fitted to MEA speciation data & Direct carbamate NMR/speciation targets in Tier A local data; the MEAH+/MEACOO- interaction was fitted with the same subset. \\
MEACOO- & \makecell[l]{dielc, f\_solv,\\z, MW} & ionic conventions plus corrected molecular weight & All ions use relative dielectric constant 8 and $f\_solv=1$ in SSM+DS; MW is corrected to MEA+CO2-H = 0.10408 kg/mol. \\
HCO3- & \makecell[l]{s, e, d\_born,\\dielc, f\_solv,\\z, MW} & literature-backed diagnostic set plus trace Born fit & HCO3- uses Held/Uyan $\sigma=2.9296$, $\epsilon/k=70.00$, and water-ion $k_{ij}=0.0$; a Tier A trace-carbonate Born fit returned $d\_born=2.9990$, so the adopted value remains 3.0. \\
CO3\textasciicircum{}2- & \makecell[l]{s, e, d\_born,\\dielc, f\_solv,\\z, MW} & literature-backed diagnostic set plus trace Born fit & CO3\textasciicircum{}2- uses Held/Uyan $\sigma=2.4422$, $\epsilon/k=249.26$, and water-ion $k_{ij}=-0.25$; a Tier A trace-carbonate Born fit returned $d\_born=2.9998$, so the adopted value remains 3.0. \\
H3O+ & \makecell[l]{s, e, d\_born,\\dielc, f\_solv,\\z, MW} & literature-backed diagnostic set with SSM+DS Born value & H3O+ is the runtime proton carrier for H+ activity; it uses Held/Uyan $\sigma=3.4654$, $\epsilon/k=500.00$, water-ion $k_{ij}=0.25$, and Figiel $d\_born=1.218$. \\
OH- & \makecell[l]{s, e, d\_born,\\dielc, f\_solv,\\z, MW} & literature-backed diagnostic set plus hydration Born derivation & OH- uses Held/Uyan $\sigma=2.0177$, $\epsilon/k=650.00$, and water-ion $k_{ij}=-0.25$; $d\_born=3.0811$ is derived by Born hydration-energy inversion and is not an MEA-system regression. \\
\bottomrule
\end{longtable}
\endgroup
